%-----------PROJECTS-----------%
\section{Projects}
\resumeSubHeadingListStart

   \resumeProjectHeading
    {\evwork{kioskvisionai}{\textbf{KioskVisionAI (Cloud-Native .NET Aspire + Azure Vision AI)}} \emph{}}{}
    \resumeItemListStart
        \resumeItem{Developed a distributed application using \textbf{.NET Aspire}, leveraging its orchestration, observability, and service discovery features to manage multiple kiosk services at scale.}
        \resumeItem{Integrated Azure Vision AI, Blob Storage, and Queues for automated image analysis, metadata enrichment, and event-driven notifications.}
        \resumeItem{Implemented cloud-native deployment with \textbf{Azure Developer CLI (azd)} — first provisioning and deploying the application, then auto-generating GitHub Actions workflows for continuous delivery to Azure.}
        \resumeItem{Result: Achieved a streamlined DevOps pipeline with reduced manual configuration, faster deployments, and improved observability across microservices.}
    \resumeItemListEnd




    \resumeProjectHeading
    {\evwork{ach-payment-integration}{\textbf{ACH Payment Integration Onetime and Recurring}} \emph{}}{}
    \resumeItemListStart
        \resumeItem{Implemented secure ACH payment workflows for donation kiosks and recurring billing using the Stripe and AuthNet API.}
        \resumeItem{Enhanced reliability, automation, and compliance in payment processing for U.S.-based mosque clients.}
    \resumeItemListEnd

    \resumeProjectHeading
    {\evwork{remote-kiosk-management}{\textbf{Remote Kiosk Device Management System}} \emph{}}{}
    \resumeItemListStart
        \resumeItem{Developed a web-based management portal to monitor and control kiosk devices in real time.}
        \resumeItem{Integrated REST APIs from KLR to provide device insights (battery, Wi-Fi, uptime) and remote commands (reboot, screenshot).}
    \resumeItemListEnd

    \resumeProjectHeading
    {\evwork{data-import-automation}{\textbf{Data Import and Automation for School/Membership Onboarding}} \emph{}}{}
    \resumeItemListStart
        \resumeItem{Built automated SQL Server data pipelines to process and validate client Excel templates for school and membership data onboarding.}
        \resumeItem{Reduced onboarding time significantly while ensuring schema validation and consistency.}
    \resumeItemListEnd



    \resumeProjectHeading
    {\evresearch{quantum-machine-learning-thesis}{\textbf{Machine learning in the realm of quantum: state of the art, challenges, future vision, and applications of it}} \emph{(Undergraduate Thesis)}}{}
    \resumeItemListStart
        \resumeItem{Overview: Outlined some recent works and different models of the
quantum machine learning, and interprets classification tasks in the realm of Quantum
with several encoding methods
}
        \resumeItem {Used Programming Language:Python, Machine Learning Framework: PyTorch, Quantum Machine Learning Framework: Pennylane, IBMQ}
    \resumeItemListEnd

% \newpage

    \resumeProjectHeading
    {\evresearch{bangla-pos-tagging}{\textbf{Bangla Parts of Speech Tagging Using Supervised Learning and Knowledge Distillation}} \emph{}}{}
    \resumeItemListStart
         \resumeItem{Overview: Developed a machine learning model for Bangla parts of speech tagging, addressing data imbalance issues by employing a knowledge distillation approach. Utilized a decision tree model as a teacher and distilled its knowledge to a neural network student model, improving tagging accuracy and efficiency.}
        \resumeItem{Used Programming Language: Python, Machine Learning Framework: PyTorch, ScikitLearn, Hugging Face, BERT}
    \resumeItemListEnd

    \resumeProjectHeading
    {\evwork{startup-success-prediction}{\textbf{Startups Success Prediction using Ensemble Classification}} \emph{}}{}
    \resumeItemListStart
        \resumeItem{Developed a machine learning model to predict the success of startups by analyzing various factors affecting their performance.}
        \resumeItem{Implemented multiple classification algorithms, including Adaboost, RandomForest, LGBM, Decision Tree, SVM, Extra Tree, and an Ensemble Voting Classifier.}
        \resumeItem{Evaluated and compared models to determine the most effective approach for accurate predictions.}
        \resumeItem{The project aimed to provide insights for entrepreneurs and investors to make data-driven decisions based on key startup attributes.}
        \resumeItem{Used Programming Language: Python, Machine Learning Framework and Libraries: ScikitLearn, Pandas, Matplotlib, Seaborn}
    \resumeItemListEnd
    
    % \pagebreak
    
    \resumeProjectHeading
    {\textbf{Software Digitization Service} \emph{}}{}
    \resumeItemListStart
        \resumeItem{Overview: Designed and developed a software solution to digitize and manage offline documents for the finance department, enabling centralized storage, easy access, and efficient retrieval of records. The project included a web application.}
         \resumeItem{Some Features:
            \begin{itemize}
                \item Supported digital conversion of paper documents and integration with existing and new users.
                \item Allowed users and administrators to upload, manage, and retrieve documents securely and efficiently.
                \item Integrated robust indexing and search functionality for quick access to digitized files.
            \end{itemize}
        }
        \resumeItem{Role: Involved in software requirements specification (SRS), system design specification (SDS), and implementation.}
        \resumeItem{Used Programming Languages: Python; Frontend: HTML, CSS, JavaScript; Backend: Django; Database: MySQL}
    \resumeItemListEnd

\resumeProjectHeading
    {\evwork{multi-output-cnn}{\textbf{Age, Gender, and Race Estimation with Multi-Output CNN Architecture}}}{}
    \resumeItemListStart
        \resumeItem{Overview: Developed a deep learning model using a multi-output Convolutional Neural Network (CNN) to estimate age, gender, and race from facial images. The project aimed to extract key demographic information, a crucial soft biometric trait for identification and demographic analysis.}
        \resumeItem{Challenges: Addressed the subtle variations in facial features caused by age, gender, and race differences, making the task more complex compared to other pattern recognition problems like object classification.}
        \resumeItem{Technologies: Deep Learning, Convolutional Neural Networks (CNN), Python, TensorFlow/Keras}
    \resumeItemListEnd

\resumeProjectHeading
    {\textbf{REST API, Database, and Gmail API Testing with Rest Assured, SQL, and Aquality}}{}
    \resumeItemListStart
        \resumeItem{Overview: Developed comprehensive test suites to validate REST APIs, database operations, and Gmail API interactions. The project ensured robust testing of backend services, focusing on verifying API responses, data integrity, and seamless integration with third-party services.}
        \resumeItem{Technologies: Java, REST Assured, SQL, Aquality Framework, TestNG, Maven, Postman.}
    \resumeItemListEnd

\resumeProjectHeading
    {\textbf{Steam Web App Testing with Selenium and TestNG}}{}
    \resumeItemListStart
        \resumeItem{Overview: Conducted extensive automated testing for the Steam web application to ensure a smooth user experience across different functionalities, including browsing, purchasing, and user account management.}
        \resumeItem{Technologies: Java, Selenium, TestNG, Maven.}
    \resumeItemListEnd

\resumeProjectHeading
    {\textbf{UI Testing with Aquality Framework}}{}
    \resumeItemListStart
        \resumeItem{Overview: Automated UI testing for a complex web application using the Aquality framework, focusing on validating user interactions, responsive design, and overall system reliability.}
        \resumeItem{Technologies: Java, Aquality Framework, TestNG, Maven.}
    \resumeItemListEnd



\resumeSubHeadingListEnd